NLP and NER

### 2021-10-13 NER_analysis_final.Rmd
NER Analysis Completed

ggRadar(
  data = radar_facet,
  mapping = aes(color = title, facet = words),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)
```

@@

```{r message=FALSE}
radar_facet_sentiment <- entities_matches_sentiment %>%
  #Change filter to locations for locations
  filter(kind == "person") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>%
  arrange(desc(sentiment))  %>%
  head(10)  %>% #Change number to include more or fewer entities
  select(-positive, -negative, -sentiment, -kind)

tender_is_the_night_protagonist <- entities_matches_sentiment %>% filter(title == "Tender is the Night") %>%
  #Change filter to locations for locations
  filter(words == "Dick Diver") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

the_great_gatsby_protagonist <- entities_matches_sentiment %>%
  #Change filter to locations for locations
  filter(words == "Gatsby") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% filter(title == "The Great Gatsby") %>% select(-positive, -negative, -sentiment, -kind)

@@

data_for_anthony <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Antho"), ] %>% filter(title == "The Beautiful and Damned") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

data_for_amory <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Amor"), ] %>% filter(title == "This Side of Paradise") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

@@

data_for_henry <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Cath"), ] %>% filter(title == "A Farewell to Arms") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

@@

ggRadar(
  data = protag_fitz %>% select(-total),
  mapping = aes(color = protagonist, facet = protagonist),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)
```

>>>>

ggRadar(
  data = radar_facet,
  mapping = aes(color = title, facet = words),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 1,
  legend.position = "right"
)
```

@@

```{r message=FALSE}
radar_facet_sentiment <- entities_matches_sentiment %>%
  #Change filter to locations for locations
  filter(kind == "person") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>%
  arrange(desc(sentiment))  %>%
  head(10)  %>% #Change number to include more or fewer entities
  select(-positive, -negative, -sentiment, -kind) %>% mutate(total = rowSums(across(where(is.numeric)))) %>% mutate(across(anger:trust, .fns = ~ round((. / total) * 100)))

sentiment_Dick_Diver <- entities_matches_sentiment %>% filter(title == "Tender is the Night") %>%
  #Change filter to locations for locations
  filter(words == "Dick") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

sentiment_Gatsby <- entities_matches_sentiment %>%
  #Change filter to locations for locations
  filter(words == "Gatsby") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% filter(title == "The Great Gatsby") %>% select(-positive, -negative, -sentiment, -kind)

@@

sentiment_Anthony <- entities_matches_sentiment %>% filter(words == "Anthony") %>% filter(title == "The Beautiful and Damned") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

sentiment_Amory <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Amor"), ] %>% filter(title == "This Side of Paradise") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

@@

sentiment_Henry <- entities_matches_sentiment[str_detect(entities_matches_sentiment$words, "Henry"), ] %>% filter(title == "A Farewell to Arms") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

all_protag <- bind_rows(sentiment_Gatsby, sentiment_Anthony, sentiment_Amory, sentiment_Dick_Diver) %>% mutate(total = rowSums(across(where(is.numeric)))) %>% mutate(across(anger:trust, .fns = ~ round((. / total) * 100)))

@@

ggRadar(
  # Add select(-total)
  data = all_protag %>% select(-total),
  mapping = aes(color = title, facet = words),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)
```

```{r graphs_hemingway}
sentiment_Henry <- entities_matches_sentiment %>% filter(title == "A Farewell to Arms") %>%
  #Change filter to locations for locations
  filter(words == "Henry") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

sentiment_Robert <- entities_matches_sentiment %>% filter(title == "For Whom The Bell Tolls") %>%
  #Change filter to locations for locations
  filter(words == "Robert Jordan") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

sentiment_Jake <- entities_matches_sentiment %>% filter(title == "The Sun Also Rises") %>%
  #Change filter to locations for locations
  filter(words == "Barnes") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

sentiment_David <- entities_matches_sentiment %>% filter(title == "The Garden of Eden") %>%
  #Change filter to locations for locations
  filter(words == "David") %>%
  group_by(title, words, kind) %>%
  summarise(across(anger:sentiment, sum)) %>% select(-positive, -negative, -sentiment, -kind)

all_protag_h <- bind_rows(sentiment_Henry, sentiment_Robert, sentiment_Jake, sentiment_David) %>% mutate(total = rowSums(across(where(is.numeric)))) %>% mutate(across(anger:trust, .fns = ~ round((. / total) * 100)))

ggRadar(
  # Add select(-total)
  data = all_protag_h %>% select(-total),
  mapping = aes(color = title, facet = words),
  rescale = FALSE,
  interactive = TRUE,
  use.label = TRUE,
  size = 2,
  legend.position = "right"
)
